Bayesim: a tool for adaptive grid model fitting with Bayesian inference

### 2018-09-07 paper/Manuscript.tex
minor manuscript updates

 \begin{figure}
   \includegraphics[width=0.9\columnwidth]{figure_1.png}
   \caption{a) High-level flowchart of inputs and outputs to \texttt{bayesim}, b) 2D schematic of adaptive grid sampling approach.}
   \label{fig1}
 \end{figure}

>>>>

 \begin{figure}
   \includegraphics[width=0.9\columnwidth]{figure_1.png}
   \caption{a) High-level flowchart of inputs and outputs to \texttt{bayesim}. Observed data as a function of experimental conditions and modeled data over those same conditions as well as fitting parameters are fed in, and the code produces a probability distribution over the fitting parameter values. b) 2D schematic of adaptive grid sampling approach, illustrating progressive subdivision in higher-probability regions of parameter space.}
   \label{fig1}
 \end{figure}
